Representation Learning for Generalized Planning - SAT Encodings

### 2021-05-05 doc/paper/paper.tex
changes

\section{Learning of Generalized Features \& Policy in Adversarial FOND domains}

@@

@@

\subsection{Fixed Pool $A$ of actions}

We here assume that all instances $P$ of the generalized problem have the same fixed set of actions $A$.
We denote by $(s, a, s'') \in T$ tuples of state, action, and possible state $s''$ resulting from the adversary
response to the application of $a$ in $s$.

\subsubsection{Variables}

\begin{itemize}
 \item $Good(s, a)$ for $s$ alive, solvable, and $a \in A$.

@@

>>>>

\section{Learning of Generalized Features \& Policy in FOND domains unsipervised}

@@

\paragraph{Bad'}

@@

\subsection{Encoding for FOND domains}

We here assume that all instances $P$ of the generalized problem have a set of actions $A$.
We denote by $(s, a, s') \in T$ tuples of state, action, and possible state $s'$ resulting from executing $a$ in $s$.

\subsubsection{Main Variables}

\begin{itemize}
 \item $Good(s, a)$ for $s$ alive, solvable, and $a \in A$.
 \item $Good(s, a, s')$ for $s$ alive, solvable, and $a \in A$.

@@

\smallpar{C1}
The policy has to be complete with respect to all alive states:
\begin{align}
\bigvee_{s' \text{ s.t. } (s, s') \in T \setminus \badtx} Good(s, s'),&\;\; \text{for $s$ alive.}
\end{align}
